Light inextensible strings under tension in the Schwarzschild geometry

### 2019-05-21 string_jpam.tex
fixes #15

\begin{abstract}
Here I analyze the behaviour of stationary, light inextensible strings
under tension in the vicinity of a nonrotating black hole.  Such
strings minimize their proper length, given by integrating the spatial
component of the Schwarzschild metric along the string.  The path is
calculated by numerical solution to the Euler-Lagrange equations.  If
the string is entirely outside the event horizon, its closest approach
is to the singularity is tangential; if the distance of closest
approach is less than about $1.076109317$ Schwarzschild radii, the
string self-intersects.  If the string attains $r=2GM/c^2$, then it
will in general be tangential to the event horizon.  Light taut
strings interpret the concept ``straight line'' and their behaviour
suggests a possible way of manipulating a black hole.
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

@@

We first consider strings for which $r>1$ everywhere (that is,
completely exterior strings).
Figure~\ref{closest_approach_non_self_intersecting} shows a sequence
of non-self-intersecting numerical solutions to
equation~\ref{rdashdash}, rotated so that the tangential point of
closest approach occurs at~$\phi=0$.
Figure~\ref{closest_approach_self_intersecting} shows the
corresponding diagram for self-interesecting strings
(Figure~\ref{light_closest_approach} shows equivalent null geodesics
for comparison).  A bisection technique reveals that if the closest
approach is greater than a critical value of~$\simeq 1.076109317(1)$,
the string does not self-intersect; if the closest approach is less
than this value, then the string crosses itself at~$\phi=\pi/2$.  As
discussed above, if $\left(r'\right)^2=2r(r-1)$, the string has a
point of inflection at which point the radius of curvature becomes
infinite.  Figure~\ref{curvature_switch} shows non-self intersecting
strings rotated so that the point of inflection occurs at~$\phi=0$; we
see that each string has a finite length in which it is convex to the
origin and two semi-infinite stretches in which the curvature is
negative.

>>>>

\begin{abstract}
Here I analyze the behaviour of stationary, light inextensible strings
under tension in the vicinity of a nonrotating black hole.  Such
strings minimize their proper length, given by integrating the spatial
component of the Schwarzschild metric along the string.  The path is
calculated by numerical solution to the Euler-Lagrange equations.  If
the string is entirely outside the event horizon, its closest approach
is to the singularity is tangential; if the distance of closest
approach is less than about $1.0761$ Schwarzschild radii, the
string self-intersects.  If the string attains $r=2GM/c^2$, then it
will in general be tangential to the event horizon.  Light taut
strings interpret the concept ``straight line'' and their behaviour
suggests a possible way of manipulating a black hole.
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

@@

We first consider strings for which $r>1$ everywhere (that is,
completely exterior strings).
Figure~\ref{closest_approach_non_self_intersecting} shows a sequence
of non-self-intersecting numerical solutions to
equation~\ref{rdashdash}, rotated so that the tangential point of
closest approach occurs at~$\phi=0$.
Figure~\ref{closest_approach_self_intersecting} shows the
corresponding diagram for self-interesecting strings
(Figure~\ref{light_closest_approach} shows equivalent null geodesics
for comparison).  A bisection technique reveals that if the closest
approach is greater than a critical value of about~$\simeq 1.0761$,
the string does not self-intersect; if the closest approach is less
than this value, then the string crosses itself at~$\phi=\pi/2$.  As
discussed above, if $\left(r'\right)^2=2r(r-1)$, the string has a
point of inflection at which point the radius of curvature becomes
infinite.  Figure~\ref{curvature_switch} shows non-self intersecting
strings rotated so that the point of inflection occurs at~$\phi=0$; we
see that each string has a finite length in which it is convex to the
origin and two semi-infinite stretches in which the curvature is
negative.
